### 2018-05-02 paper/evaluation.tex
removed sections
wrote a bit and experiments are undergoing
added figure

\subsection{Devices' predictions of the user behavior} % (fold)
\label{sub:devices_predictions_of_the_user_behavior}

\commentAL{Will probably ditch that}

% subsection devices_predictions_of_the_user_behavior (end)
%\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). We see that the number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
\end{figure}

@@

\commentAL{Git-noobiness removed my data: it has to compute again overnight.}

>>>>

% \subsection{Devices' predictions of the user behavior} % (fold)
% \label{sub:devices_predictions_of_the_user_behavior}

% Adios, section

%\commentAL{Should evaluate the inference of the model given only the observable sequence. Also show that $P[O_{t+1} | S_t] \simeq P[O_{t+i} | S_t]$}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/nodes_per_layer_vs_theta.pdf}
\caption{\label{fig:nodes_per_layer_vs_theta}Number of nodes per layer of POR as a function of the parameter $\theta$ (the maximal probability that all nodes in a layer fail at once). The number of nodes logarithmically decreases as we relax the $\theta$ constraint.}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figures/transfer_time_vs_size.pdf}

\caption{\label{fig:transfer_time_vs_size}Files' transfer time as a function of their size, along with a log-linear regression of the same data.}
\end{figure}
